\documentclass[11pt,a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage[finnish]{babel}
\usepackage[T1]{fontenc}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{url}
\pagestyle{plain}
\usepackage{graphicx}
\title{The Analysis of Three Substances }
\author{Delun Li\\014631300\\Orgaanisen kemian työt 1\\Työ 5}
\date{25.10.2018}


\begin{document}

\maketitle

\pagebreak


\section{Introduction}

In this experiment a unknown liquid substance has been given. The task was to extract and identify the three unknown substances. The substances were cleaned either with distillation or recrystallizing it. By extracting the solution first with NaHCO$_3$ carboxylic compounds can be separated from the solution. Following by with NaOH and lastly with HCl, phenols and amides can be separated from the solution. After every extraction the water layer is then extracted with ether (30 ml). With this process the excessive organic compounds can be separated thoroughly.  

\section{Pre Tests }

Before doing any experiments on the unknown solution, IR- and $^1$H-NMR spectrums were taken. Some pre tests were done to confirm what organic compounds could there possibly have. Using NaHCO$_3$ acidic compunds can be indicated, amides with CuSO$_4$ and phenols with FeCl$_3$. In positive reactions carboxylic compounds bubbles in the test tube, in amides test the solution will change it's color to either green or blue and in phenol test Fe$^{+3}$ ions will cause color changes in the solution. All the pre tests came out negative. 

\section{The Work Execution}

After the pre tests the solution was extracted into diethylether (50 ml) and afterwards 2M NaHCO$_3$ (3x50 ml). The ether layer then extracted with 2M NaOH (2x50 ml) and lastly with 4M HCl (3x40 ml). The water layers extracted from NaHCO$_3$ (\textbf{1}), NaOH (\textbf{2}) and HCl (\textbf{3}) are recovered and later analyzed. After each extraction ether solution (\textbf{4}) is left. 

Due to the fact from the previous pre tests \large-there were no indication of any acidic, amides or phenol compounds in the solution\large- 
I started analyzing solution \textbf{4}. The ether solution were dried over with MgSO$_4$ and then recover the neutral compounds from the distillate. Ether (boiling point b.p $\approx 35 ^{\circ}$C) distilled first and subsequently \textbf{liquid 1}(b.p $\approx 75 ^{\circ}$C) was distilled and lastly \textbf{liquid 2} (b.p $\approx 152 ^{\circ}$C). 
\end{document}
